The Role of Video Data Sharing in Advancing Education Policy and Practice

### 2015-05-10 2015-06-01-nsf-ed-workshop/paper.tex
more blue sky thoughts in conclusion

As Gesell once noted, cameras can record behavior in ways that make it "...as tangible as tissue." \cite{Scott2011}.

Video has considerable untapped potential for making tangible the anatomy of successful teaching and learning.
Realizing this potential requires a multifaceted approach that reduces barriers to sharing video and fosters new community values that embrace it.
The Databrary project has built technology and policies that overcome many of the most significant barriers to widespread video data sharing within the developmental sciences community, including solutions to maintaining participant privacy, data tagging, and data management. 
Databrary suggests ways that video and other identifiable data collected in the context of education research might also be shared.
Technologies and policies for providing secure access to videos for broader use cases will have to be developed, and tools that allow desktop coding software files to be seamlessly imported to and exported from Databrary will have to be perfected.
Communities of scholars dedicated to sharing education-related video will have to be cultivated.
But, we believe that the widespread sharing of high value, high impact data of the sort that video can provide promises to advance education policy and improve practice.
The Databrary team welcomes collaborations with other like-minded parties who share our vision \cite{Adolph2012} for a future where open data sharing is the norm.

>>>>

Imagine a time in the near future when researchers interested in studying classroom teaching and learning can mine an integrated, synchronized, interoperable, and open data set.
That data set includes multiple measurements -- video from multiple cameras, eye tracking, motion, and physiological measurements, and both historical and real-time student performance data.
Imagine that this classroom-level data can be linked with grade, school, neighborhood, community, region, and state-level data about education practice, curriculum, and policy.
Then, imagine training a cadre of experts with skills in the data science of learning and education who are made keenly sensitive to privacy, confidentiality and ethical issues involved in research involving sensitive, identifiable information.
We then empower these learning scientists to extract from the data meaningful insights about how educational practice and policy might be improved.
In short, imagine a science of teaching and learning that can be personally tailored to individuals in ways analogous to the impact of big data on medicine \cite{BBC2014}.
The barriers to realizing this vision are similar to those that confront the vision of personalized medicine -- the development of technologies that enable data to be collected, synchronized, tagged, curated, stored, shared, linked, and aggregated, policies and practices that ensure security and individual privacy, and the cultivation of professional expertise needed to turn raw data into actionable insights.

As Gesell once noted, cameras can record behavior in ways that make it "...as tangible as tissue." \cite{Scott2011}.
The Databrary team contends that video has a central role to play in efforts to make tangible the anatomy of successful teaching and learning.
In fact, we argue that video could be the core around which other measures of teaching and learning cluster.
This requires reducing barriers to sharing video and related data and one that fosters new community values around ethical data sharing.
The Databrary project has built technology and policies that overcome many of the most significant barriers to widespread sharing within the developmental sciences community, including solutions to maintaining participant privacy, data tagging, and data management. 
Databrary suggests ways that video and other identifiable data collected in the context of education research might also be shared.
Technologies and policies for providing secure access to videos for broader use cases will have to be developed,  tools that allow desktop coding software files to be seamlessly converted to and from one another will have to be perfected, and ways of synchronizing and linking disparate data streams will have to be created.
Equally important, communities of scholars dedicated to collecting, sharing, and mining education-related video data will have to be cultivated.
But, we believe that the widespread sharing of high value, high impact data of the sort that video can provide promises to advance education policy and improve practice.
The Databrary team welcomes collaborations with other like-minded parties who share our vision \cite{Adolph2012} for a future where open video data sharing is the norm and a personalized science of teaching and learning is the goal.
